---
title: "lab9"
author: "Zachary Muller"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Q1
```{r}
getwd()
```

# Q2

- A will take a sample that is of size = iter * n, from data held in x with replacement and store the data in y

- B forms a condfidence interval.

- Equal probability sampling is necessary to have a normal distribution.

```{r}
set.seed(35)
sam=round(rnorm(20,mean=10,sd=4),2)
unique(sample(sam,20,replace=TRUE) )
unique(sample(sam,20,replace=TRUE) )
unique(sample(sam,20,replace=TRUE) )
unique(sample(sam,20,replace=TRUE) )
unique(sample(sam,20,replace=TRUE) )
```

- We can see that we are getting less than 20 unique values and this is due to the replacement of values when they are drawn. 

```{r}
unique(sample(sam,20,replace=FALSE) )
unique(sample(sam,20,replace=FALSE) )
unique(sample(sam,20,replace=FALSE) )
unique(sample(sam,20,replace=FALSE) )
unique(sample(sam,20,replace=FALSE) )
```

- We know can see 20 values because we are not replacing anything. 

```{r}
#sample(sam, 21, replace=FALSE)
```

- The code does not run because we are requesting a sample size larger than the population, and we are not replacing anything. 

# Q3

```{r}
myboot2<-function(iter=10000,x,fun="mean",alpha=0.05,cx=1.5,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size

y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=cx)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=cx)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=cx)

invisible(list(ci=ci,fun=fun,x=x))# Some output to use if necessary
}
```

```{r}
# rnorm
set.seed(39)
sam = rnorm(25,mean=25,sd=10)
mean(sam)
catch <- myboot2(sam,iter = 10000, alpha = .05)

#rchisq
set.seed(30)
sam = rchisq(20,df=3)
mean(sam)
catch <- myboot2(sam,iter = 10000, alpha = .05)

#rgamma
set.seed(40)
sam = rgamma(30,shape=2, scale=3)
mean(sam)
catch <- myboot2(sam,iter = 10000, alpha = .05)

#rbeta
set.seed(10)
sam = rbeta(20, shape1=3, shape2=4)
mean(sam)
catch <- myboot2(sam,iter = 10000, alpha = .05)
```

- The point estimate value is the population value but rounded.

- Yes the population value is in each interval. 

```{r}
# rnorm
set.seed(39)
sam = rnorm(25,mean=25,sd=10)
mean(sam)
catch <- myboot2(sam,iter = 10000, alpha = .2)

#rchisq
set.seed(30)
sam = rchisq(20,df=3)
mean(sam)
catch <- myboot2(sam,iter = 10000, alpha = .2)

#rgamma
set.seed(40)
sam = rgamma(30,shape=2, scale=3)
mean(sam)
catch <- myboot2(sam,iter = 10000, alpha = .2)

#rbeta
set.seed(10)
sam = rbeta(20, shape1=3, shape2=4)
mean(sam)
catch <- myboot2(sam,iter = 10000, alpha = .2)
```

# Q4
```{r}
myboot2<-function(iter=10000,x,fun="mean",alpha=0.05,cx=1.5,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size

y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=cx)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=cx)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=cx)

invisible(list(ci=ci,fun=fun,x=x, xstat=xstat))# Some output to use if necessary
}
```

```{r}
sam <- c(1,1,1,2,2,2,2,3,3,4,4)
booty <- myboot2(x=sam, fun="median")
```

- Interval is [1, 3]

# Q5
```{r}
set.seed(39)
sam = rnorm(25, mean=25, sd=10)

norms = myboot2(x=sam, fun=function(x) {mean(x) / median(x)}, alpha = 0.05, xlab="Mean(x)/Median(x)", col="Blue")

set.seed(30)
sam = rchisq(20,df=3)

chisqs = myboot2(x=sam, fun=function(x) {mean(x) / median(x)}, alpha = 0.05, xlab="Mean(x)/Median(x)", col="Purple")

set.seed(40)
sam = rgamma(30,shape=2, scale=3)

gammas = myboot2(x=sam, fun=function(x) {mean(x) / median(x)}, alpha = 0.05, xlab="Mean(x)/Median(x)", col="Cyan")

set.seed(10)
sam= rbeta(20, shape1=3, shape2=4)

betas = myboot2(x=sam, fun=function(x) {mean(x) / median(x)}, alpha = 0.05, xlab="Mean(x)/Median(x)", col="Red")



set.seed(39)
sam = rnorm(25, mean=25, sd=10)

norms = myboot2(x=sam, fun=function(x) {mean(x) / median(x)}, alpha = 0.3, xlab="Mean(x)/Median(x)", col="Cyan")

set.seed(30)
sam = rchisq(20,df=3)

chisqs = myboot2(x=sam, fun=function(x) {mean(x) / median(x)}, alpha = 0.3, xlab="Mean(x)/Median(x)", col="Red")

set.seed(40)
sam = rgamma(30,shape=2, scale=3)

gammas = myboot2(x=sam, fun=function(x) {mean(x) / median(x)}, alpha = 0.3, xlab="Mean(x)/Median(x)", col="Brown")

set.seed(10)
sam= rbeta(20, shape1=3, shape2=4)

betas = myboot2(x=sam, fun=function(x) {mean(x) / median(x)}, alpha = 0.3, xlab="Mean(x)/Median(x)", col="Purple")
```


# Q6
```{r}
?distributions
```

```{r}
# Poisson Poisson Poisson
samp = rpois(20, lambda = 4)

meansbooty <- myboot2(samp, iter=10000, fun="mean", alpha=.2)

varsbooty <- myboot2(samp, iter=10000, fun="var", alpha=.2)

# WEIB
samp = rweibull(20, scale=2, shape=4)

meansbooty <- myboot2(samp, iter=10000, fun="mean", alpha=.2)

varsbooty <- myboot2(samp, iter=10000, fun="var", alpha=.2)


# CAUCHY CAUCHY CAUCHY
samp = rcauchy(20, location=2, scale=3)

meansbooty <- myboot2(samp, iter=10000, fun="mean", alpha=.2)

varsbooty <- myboot2(samp, iter=10000, fun="var", alpha=.2)

# exponential :(
samp = rexp(20)

meansbooty <- myboot2(samp, iter=10000, fun="mean", alpha=.2)

varsbooty <- myboot2(samp, iter=10000, fun="var", alpha=.2)
```

# Q7
```{r}
set.seed(68)
sam=rnorm(20,mean=10,sd=4)
myboot2(sam,iter=10000, fun="sd",alpha=.05)
myboot2(sam,iter=10000, fun="median",alpha=.05)
myboot2(sam,iter=10000,fun="mean",alpha=.05)
```

# Q8
```{r}
df <-read.csv("FATAL.csv")
packagedeal::myboot2(x=df$Fatalities)
```

# Q9
```{r}
myboot2<-function(iter=10000,x,fun="mean",alpha=0.05,cx=1.5,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size

y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=TRUE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=cx)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=cx)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=cx)

invisible(list(ci=ci,fun=fun,x=x))# Some output to use if necessary
}

set.seed(90)
sam=rnorm(50,mean=22,sd=6)
myboot2(sam,iter=100000, fun="sd",alpha=.45)
myboot2(sam,iter=100000, fun="median",alpha=.45)
myboot2(sam,iter=100000,fun="mean",alpha=.45)
```
