---
title: "Ass3"
author: "Zachary Nuller"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Q1

- 2 minutes == 120 seconds, set rate to 1/95

## A

```{r}
1 - pexp(120, 1/95)
```

## B

```{r}
df <- read.csv("PHISHING.CSV")
(mean(df$INTTIME)-95)/95
(var(df$INTTIME)-9025)/9025
```


The mean and variation show us that is follows an exponential disitrubition for beta = 95

# Q2

## A

```{r}
alpha = 3
beta = 0.07 

alpha * beta

alpha * (beta * beta)
```

## B

- No, you would not expect a value that high from our gamma distribution. 3STD should gives us a range to .57mil. .6 mil is just outside of our range, and is an outlier. It is not expected to have that much water. 


# Q3

## A

$mean_a = 2*2 = 4$

$mean_b = 1*4 = 4$

## B

$sigma_a = 2*2^2 = 8$

$sigma_b = 1*4^2 = 16$

## C

```{r}
pgamma(1,2,1/2)
pgamma(1,1,1/4)
```

B is much more likely to cause a reaction as B is at roughly 22%, and A is at roughly 9%.


# Q4 

## A

```{r}
pweibull(2,2,2)
```


## B

$2*.88623 = 1.77246$

$4(1-0.88623^2) = .8583$

## C

```{r}
pweibull(3.62546,2,2) - pweibull(-0.08054,2,2)
```

The probability is .962

## D


```{r}
1-pweibull(6,2,2)
```

- Highly unlikely. 

# Q5

## A

$mean=2/11 = .18182$ 

$variance=18/{{11^2(11)}} = 0.01240$

## B

```{r}
1-pbeta(.4,2,9)
```

## C

- Can use pbeta again to find P(<=1)

```{r}
pbeta(.1, 2, 9)
```


# Q6

## A

- alpha = 2, beta = 16

## B

$4*.88623 = 3.54492$

$16(1-.88623^2)=3.4335$



## C

- Can use pweibull to calculate to find the probability that a chip will not fail. 

```{r}
1-pweibull(6,2,4)
```

# Q7

## A

$p(x, y) = \frac{1}{36}$ 

## B
$P(X=1) = p_1(1) = 1/36 * 6 = 1/6$

$p_1(X) = 1/6$

$P(Y=1) = p_2(1) = 1/36 * 6 = 1/6$

$p_2(Y) = 1/6$

## C
$p1(x|y) = (1/36)/(1/6) = 1/6$

$p2(x|y) = (1/36)/(1/6) = 1/6$


## D

- x and y are independent because the result of the other event does not affect the result of the event at hand. 


# Q8

## A

```{r}
time1<- c(1/7,2/7,1/7)
time2<- c(0,0,2/7)
time3<- c(0,0, 1/7)
time1
time2
time3
```

## B

```{r}
time1<- c(1/7,2/7,1/7)
time2<- c(0,0,2/7)
time3<- c(0,0, 1/7)
time1
time2
time3

c(time1[1]+time2[1]+time3[1],time1[2]+time2[2]+time3[2],time1[3]+time2[3]+time3[3])
```


## C

```{r}
time1<- c(1/7,2/7,1/7)
time2<- c(0,0,2/7)
time3<- c(0,0, 1/7)
time1 = c(time1,sum(time1[1],time1[2],time1[3]))
time2 = c(time2,sum(time2[1],time2[2],time2[3]))
time3 = c(time3,sum(time3[1],time3[2],time3[3]))
time1
time2
time3
```

## D

- n/a

# Q9

## A

$f_2(y)= \int_y^{2y}f(x,y)dx $

$= \frac{e^{-y/10}}{10y}$

## B

- The expected value is beta. Beta is 10 for our problem, therefore the expected value is 10. 

# Q10

## A
$\frac{cxe^{-x^2}}{-2x}$ from 0 to inf $=1$


$0 - \frac{ce^{-0^2}}{-2} = 1$
$c/2$ = 1

$c=2$

## B

$2xe^{-x^2}/{-2x}$ from [0, inf] = 1

$0 - 2e^{-0^2}/{-2}$ = 1

## C

$f_1(x)=1$

$f_2(y|x) = 2e^{-x^2}$

# Q11

- The covariance of X,Y = E(XY) - E(X)E(Y)

- E(XY) = 0, so COV(X,Y) = 0. 

- Y is dependent on X. If x = 2, Y can only be = X or = -X.

# Q12

## A

$E(\bar{Y}) = \frac{a + b}{2} = \frac{(1 + 3)}{2} = 2$


## B

$ var(\bar{y}) = \frac{1/3}{\sqrt{60}} = 0.005556$

## C

- This puppy has a bell shape to it. We have over 30 samples, so our population is more than enough for the CLT to be applicable. 

## D

- n/a

## E

- n/a

# Q13

## A

- P(Y<=1) = P(Z<-2.9668)

```{r}
pnorm(-2.9668)
```

## B

- P(Y >= 11) = P(Z > 1.1410)

```{r}
1-pnorm(1.1410)
```

## C


```{r}
pbinom(1,20,.4)
1-pbinom(10,20,.4)
```

# Q14

## A

```{r}
df <- read.csv("LEADCOPP.csv")

t.test(df$LEAD, conf.level = 0.99)
```

## B
```{r}
t.test(df$COPPER,conf.level = 0.99)
```

## C

- 99% of lead falls within [-1.1478, 6.919]

- 99% of copper falls within [0.1518, 0.6647]

## D

- 99% of copper and lead samples are within our interval. 

# Q15

```{r}
df <- read.csv("SOLARAD.csv")

with(df, t.test(STJOS, IOWA, paired=TRUE, conf.level = 0.95))
```

- Between 156.8193 and 239.1807.


# Q16

## A

```{r}
df <- read.csv("DIAZINON.csv")

with(df, t.test(DAY, NIGHT, paired=TRUE, conf.level = 0.90))
```

## B

- The assumption is that the data has a normal distribution. 

## C

- There is always some difference. 
