---
title: "Zachary Muller Lab 2"
---
# Task 1
```{r}
getwd()
```

# Task 2
```{r}
ddt <- read.csv("EPAGAS-1.csv")
ddt6 <- head(ddt, 6)
ddt6
```

# Task 3
## Vector form
```{r}
mpgvect <- ddt$MPG
```
## transforming mpg into z
```{r}
z <- (mpgvect - mean(mpgvect))/sd(mpgvect)
```

## Verify z-bar == 0
```{r}
print(paste0("z-bar = ", round(mean(z), digits=4)), quote=FALSE)
```

## Verify sz ^2 is 1
```{r}
print(paste0("sz^2 = ", var(z)), quote=FALSE)
```

## Possible Outliers between [2,3] standard deviations 
```{r}
mpgvect[abs(z) >= 2 & abs(z) <=3]
```

## Possible outliers in z greater than 3
```{r}
mpgvect[abs(z)>3]
```

## Use lattice library to construct a plot
```{r}
library(lattice)
mycol = ifelse(abs(z)>3, "Red",
        ifelse(abs(z)>=2 &abs(z)<=3,"Blue", "Black"))  
lattice::dotplot(mpgvect, cols=mycol)
```

# Task 4
## Box plot of MPG
```{r}
boxplot(mpgvect, notch = T, horizontal = T, col= "Black", main="Boxplot of MPG")
```

## ChebyShev pediction 
The proportion of data within 2 standard deviations of mean should be 75% of the data
k = 2
1/2^2 = 1/4 = 25% are more than k deviations from the mean 


## Calculate exact proportion using R
```{r}
proportion <- mpgvect[abs(z) <= 2]
print(paste0(length(proportion),"% of data is within 2 standard deviations"))
```

## Does Chebyshev agree with the data?
```{r}
mean(abs(z- mean(z)) >= 2*sd(z)) <= 1/4
```
Yes, he does.

## Empirical Rule proportions
The empirical rule states that 95% of data should be within two standard deviations 

## How well does it correspond?
It corresponds well. We saw that 96% of data in our dataset is within two standard deviations. 

## Is the empirical rule valid in this case? Why?
The rule states that there are two assumptions.
1. It is unimodel 
2. It has symmetric distribution

Both of the assumptions hold for this case, therefore the empirical rule is valid. 







