---
title: "Zachary Muller Lab1"
---
knitr::opts_chunk$set(echo = TRUE)

# TASK 1
```{r}
getwd()
```

# TASK 2
```{r}
ddt = read.csv("DDT.csv")
head(ddt)
```
# TASK 3
### qualitative variables: RIVER, SPECIES
### quantitative: MILE, LENGTH, WEIGHT, DDT
### There are 3 unique species

## subset for LMBASS > 800:
```{r}
subset(ddt, ddt$SPECIES=="LMBASS" & ddt$WEIGHT > 800)
```
## subset for river SCM and ddt > 4.0
```{r}
subset(ddt, ddt$RIVER=="SCM" & ddt$DDT>4.0)
```

## Clicker Questions
mean length: 42.81
standard dev: 376.5461
no
last value: 1.00

# TASK 4
## Rivers table
```{r}
table(ddt$RIVER)
```
## rivers bar plot
```{r}
barplot(with(ddt,table(RIVER)),col=1:4, xlab = "Rivers", ylab = "# of fish measured")
```
## table of rivers and species
```{r}
data <- with(ddt,table(RIVER, SPECIES))
data
```
## barplot of rivers and species
```{r}
data <- with(ddt,table(RIVER, SPECIES))
barplot(data,ylim = c(0, 100), col=1:4,beside = T, legend.text = c("FCM", "LCM", "SCM", "TRM"), xlab = "Species", ylab = "# of fish measured", args.legend = list(x="topleft",title="Rivers"))
```

# TASK 5
## Pie chart for species 
```{r}
species <- with(ddt, table(SPECIES))
pie(species,col = 1:3,main = "Species distribution")
```
## pie chart for rivers
```{r}
rivers <- with(ddt, table(RIVER))
  pie(rivers,col = 1:4,main = "Distribution of rivers where fish were measured")
```

# TASK 6
## barplots for DDT, weight, and length
```{r}
layout(matrix(c(1,2,3),nr=1,nc=3))# 1 row 3 cols
with(ddt,boxplot(LENGTH,ylab="LENGTH",col="Blue",notch=TRUE))
with(ddt,boxplot(WEIGHT,ylab="WEIGHT",col="Red",notch=TRUE))
with(ddt,boxplot(DDT,ylab="DDT",col="Green",notch=TRUE))
```

# TASK 7
## Length VS Weight
```{r}
coplot(LENGTH~WEIGHT|RIVER,data=ddt)
```
## DDT VS Weight
```{r}
coplot(DDT~WEIGHT|SPECIES,data=ddt)
```

# TASK 8
## Bar
```{r}
library(ggplot2)
plt <- ggplot(ddt, aes(x=SPECIES, y=WEIGHT, fill=RIVER)) + 
  geom_boxplot() + ggtitle(label = "ZACHARY MULLER")
plt
```

## VIOLIN
```{r}
library(ggplot2)
plt <- ggplot(ddt, aes(x=RIVER, y=LENGTH, fill = SPECIES)) + 
  geom_violin() + ggtitle("ZACHARY MULLER")
plt
```
## SCATTER
```{r}
library(ggplot2)
plt <- ggplot(ddt,aes(x=WEIGHT, y= LENGTH, color=SPECIES)) + geom_point() + ggtitle("ZACHARY MULLER")
plt
```



