---
title: "Ass4"
author: "Zachary Muller"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# 10/10 done



# Q 1

## A
```{r}
mydata <- read.csv("NZBIRDS.csv")
samples <- sample(1:133, 35)
sample = mydata[samples,]
sample
```

## B
```{r}

mp <- c(-1,1)
mean(sample$Body.Mass) + mp*qt(1-.05,34)*sd(sample$Body.Mass)/sqrt(35)

```

## C 
- 95% of means of body masses will fall within our interval. (With this specific samples)

## D

- The interval contains 95% confidence, meaning that it will most likely contain the mu. 

## E
```{r}
mean(sample$Egg.Length) + mp*qt(1-.05,34)*sd(sample$Egg.Length)/sqrt(35)
```

## F
```{r}
n1 = 38 # total THAT ARE EXTINCT
n2 = 78 # total THAT ARE NOT EXTINCT

p1hat = 21 / n1  
q1hat = 1 - p1hat
p2hat = 7 / n2
q2hat = 1 - p2hat

mp = c(-1,1)
conf <- (p1hat - p2hat) + mp * qnorm(1-.05/2,0,1)*sqrt((p1hat*q1hat/n1) + (p2hat*q2hat/n2))
conf
```

## G

- Yes, the theory is supported. 

# Q2

```{r}
t.test(rnorm(100,mean=1312,sd=422),rnorm(47,mean=1352,sd=271),conf.level = .90)
```


# Q3

## A

$y \sim N(0,\sigma^2)$

$z = y/{\sigma} \sim N(0,1)$

$g(v) = GPRIME(v) = 1/\sqrt pi \sqrt 2 ^{v^{1/2 -1 e -v/2 dy}}$


## B

$ (y/lambda)^2 $
[0.0025,1] 
$(y/lambda)^2$ 
[0.0975,1]

# Q4

## A

- The null hypothesis: $\mu = 2$ and the alternative hypothesis: $\mu \neq2$

## B

- T: -1.02 P: 0.322


## C

- $|T| < 2.1262$

## D

- P > alpha so the null hypothesis can be accepted as true.


## E

- They can both use the null hypthesis against the alternative hypothesis.

# Q5

## A

- $N_s = 25, Mu = 15, sampleMean = 14.516, sampleSD = 12.9637$

$H0: mu = 15$, h1 is opposite

(xbar - mu)/S/sqrt(n) = -0.1867

$alpha = .1,p = .854$

From this, we can conclude that the sample is representative of all Wisconsin Lakes. 

## B

The likelihood is not too high.

# Q6

```{r}
q6 <- read.csv("ORCHARD.csv")
t.test(q6$CONDITION == "FOG",q6$CONDITION != "FOG",mu = 0, conf.level = .95)
```

# Q7 

## B 

```{r}
turb <- read.csv("GASTURBINE.csv")
var.test(turb[turb$ENGINE == "Traditional",]$HEATRATE,turb[turb$ENGINE == "Aeroderiv",]$HEATRATE, conf.level = .95, var.equal=T)
```

## B

```{r}
var.test(turb[turb$ENGINE=="Advanced",]$HEATRATE,turb[turb$ENGINE == "Aeroderiv",]$HEATRATE,conf.level = .95, var.equal=T)
```

# Q8

## A

 - H0: No significant difference in the variances at each site. 

H0 = sigma^2 = sigma2^2 

- H1: There is a significant different at each site. 

H1 = opposite of null

## B

```{r}
gob = read.csv("GOBIANTS.csv")
head(gob)
```

- $F = S21/S22$ so
- $F=1.0498$

## C

The rejection region is where
$F > F_{\alpha/2}$,  
being where x numerator and $x_2$ are the degrees of freedom for the numerator and denominator sample variances.

Since alpha is .5, alpha/2 is .025. 

- $F_{0.025} (25.25) = 2.23$ 
- $H_0$ is rejected when F exceeds 2.23.


## D

- F = 1.0498.


- P Value:

$P(F<1.0498) = .55$

$P(F>= 1.0498) = 1 -.55 = .45$

$ P = 2 *.45 = .9 $

## E

.05 is less than the P value of .9. This is not in the rejection region so we cannot reject the hypothesis. With 95% confidence we can say there is no significant difference between two variances at the sites.

## F

- P value greater than 0.05 


# Q9

- The Null hypthesis is $\mu = 0$ and alternative is $\mu \neq0$

```{r}
data<- read.csv("THRUPUT.csv")
t.test(data$HUMAN, data$AUTO, mu=0, paired = T)
```

# Q10

```{r}
## sample function

set.seed(35) # This will give everyone the same sample
sam=round(rnorm(30,mean=20,sd=3),3)

########### bootstrap function ##################
myboot<-function(iter=10000,x,fun="mean",alpha=0.05,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size
y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...,col = rainbow(5))
#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)
#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=3)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=3)
# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=3)
return(list(ci=ci,fun=fun,x=x, t=t))# Some output to use if necessary
}
myboot(x=sam)
```

