# Zachary Muller Lab 4

# Q1
```{r}
getwd()
```

# Q2
```{r}
spruce.df <- read.csv("SPRUCE.csv")
tail(spruce.df)
```

# Q3 

## Lowess Smoother Plot
```{r}
library(s20x)
trendscatter(Height~BHDiameter, f = 0.5, data = spruce.df)

```


## Linear Model 
```{r}
# Now make the linear model
spruce.lm=lm(Height~BHDiameter,data=spruce.df)
```

## Residuals & Fitted
```{r}
height.res <- resid(spruce.lm)
height.fit <- fitted(spruce.lm)
```

## Plot and Compare 
```{r}
plot(height.res, height.fit)
```

## Plot using Trendscatter
```{r}
trendscatter(height.res, height.fit)
```

- The shape of te new trendscatter looks a lot like a mountain to me. The curve made by the earlier plot does not level out or dip back down. It rises from left to right.

## Residual Plot
```{r}
plot(spruce.lm, which =1)
normcheck(spruce.lm,shapiro.wilk = TRUE)
```

- P value = 0.29


# Task 4
```{r}
quad.lm=lm(Height~BHDiameter + I(BHDiameter^2),data=spruce.df)
plot(Height~BHDiameter, data= spruce.df) # Fresh scatter
myplot=function(x){
  0.86089580 +1.46959217*x  -0.02745726*x^2
}

curve(myplot, lwd=2, col="steelblue",add=TRUE) # Quadratic Cruve
quad.fit = fitted(quad.lm)
plot(quad.lm, which=1) # Plot of resid vs fitted
normcheck(quad.lm,shapiro.wilk = TRUE) # P value
```

- The P value is 0.684, and we can see that there is a more straight line and could apply the straight line test. 

# Task 5
```{r}
summary(quad.lm)
```

## Bhat1, Bhat2, Bat3: BHx
- BH1: 0.860896

- BH2: 1.469592

- BH3: -0.027457

## Interval Estimates
```{r}
ciReg(quad.lm)
```

## Eq of fitted line 

- y = 0.8609+1.4696x-.0275x^2

## 15, 18, 20 predict
```{r}
predict(spruce.lm, data.frame(BHDiameter = c(15,18,20)))
```

- Quad had higher predictions


## What does multiple R squared mean in this case?

- The percentage of variation this is caused by an indepedent variable in the data. 

## Most variety in height

- quad.lm


## ANOVA
```{r}
anova(spruce.lm)
anova(quad.lm)
```


## RSS, MSS, TSS, MSS/TSS

```{r}
height.qfit=fitted(quad.lm)
TSS = with(spruce.df, sum((Height-mean(Height))^2))
TSS
MSS = with(spruce.df, sum((height.qfit-mean(Height))^2))
MSS
RSS=with(spruce.df, sum((Height-height.qfit)^2))
RSS

MSS/TSS
```


# Task 6
```{r}
cooks20x(quad.lm)
```

## What is Cooks distance?

- Cooks Distance is a commonly used estimate of the influence of a data point when performing a least-squares regression analysis

- Cooks distance is pretty high 18, 21, 24 observation numbers 

## Quad2 lm and remove highest cooks distnace 
```{r}
quad2.lm=lm(Height~BHDiameter + I(BHDiameter^2) , data=spruce.df[-24,])
summary(quad2.lm)
summary(quad.lm)
```

- The change was apparent in the summary but it was not a very drastic change.
 
 
# Task 7


# Task 8 
```{r}
library(packagedeal)
line = packagedeal::funky(10)
line
```

- Outputs a number from a formula that we used for this lab. 

 
 
 
 
