---
title: 'Ass 2: Template'
author: "Zachary Muller"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE, fig.align='center'}
knitr::opts_chunk$set(echo = TRUE)
```

# Questions{}

## Q 1

- a: The probability of not getting a correct match is 7.88%. There is a 92.12% chance of there being a correct match.

- b: The probability of a novice getting a wrong match is 25.45%.

- c: They are more likely to be a novice due to the higher chance. 


## Q 2
```{r}
plot(1:10)
```

- a: There is a 50% chance. 100 athletes using it, 50 tested positive out of the 100 testing. 50/100 = .5

- b: There is a 90% chance. 900 Non users, 9 tested positive. 891/900 = .99

- c: Bayes: $\frac{p(u)p(+|u)}{p(u)p(+|u)+p(nu)p(+|nu)}$
$p(u) = .1$, $p(nu) = .9$
$p(+|u) = \frac{\frac{50}{1000}}{.1}$, $p(+|nu) = \frac{\frac{9}{1000}}{.9}$
$p(u|+) = \frac{(.1)(.5)}{(.1)(.5)+(.9)(.01)} = .8475$

## Q 3

- The theorem states that multiplying each element in a list by each element in another list is how you get all possible combinations with a letter from each list. The total number of outcomes is determined by how many combinations there are. Additionally this can be determined by multiplying the cardinalities of each list. 
- If list x is length 4, and list y is length 5, the number of possible combinations is 4 * 5 = 20. 

## Q 4

- Let X equal a set of length 4. We want permutation of 2 from the set.

- Number of permutations = $4!/{4-2} = 24/1 = 24 $

## Q 5

A is a set of n unique items partitioned into k sets. 
$\frac{N!}{n_1!...n_k!}$

## Q 6

n items are picked - x items are not. x is N-n for N being the size of the pool.

$\frac{N!}{n!(N-n)!}$

## Q 7

- a: $.09 + .3 + .37 + .2 + .04 = 1.0$

- b: $p(x=3 \cup x=4) = .20 + .04 = .24$

- c: $p(2 > x) = .09 + .30 = .39 $

## Q 8

### a

- The first rule is that all probabilities fall within 0 <= p(y) <= 1. All probabilities fall within this range so we are good there. 
- The second rule is that the sum of all probabilities add up to one. 

- $.17+.10+.11+.11+.10+.10+.07+.05+.03+.02+.02+.02+.02+.02+.01+.01+.01+.01+.01+.005+.005 = 1.0$

### b

- We just need to sum the values from p(10) to p(20)

- $.02 + .02 + .02 + .02 + .01 + .01 + .01 + .01 + .01 + .005 + .005$

### c

- Mean

```{r}
numbers <- seq(0,20)
mu <- sum(numbers*c(.17,.10,.11,.11,.10,.10,.07,.05,.03,.02,.02,.02,.02,.02,.01,.01,.01,.01,.01,.005,.005))
mu

ysquare = numbers^2
variance <- (numbers - mu)^2 * c(.17,.10,.11,.11,.10,.10,.07,.05,.03,.02,.02,.02,.02,.02,.01,.01,.01,.01,.01,.005,.005)
variance <- sum(variance)
variance <- round(variance)
```


## 9

### A

```{r}
dbinom(10, 25, .7)

```

### B
```{r}
pbinom(5,size=25,.7)
```


### C

$25(.7) = 17.5 = mu$

$25(.7)(.3) = 5.25 = sigma^2$

$\sigma = sqrt(sigma^2) = 2.2913$


### D

- On average, 17.5 out of the 25 students will have earned their PhD. The STD is 2.2913


## 10 

### A

- N = 50 and prob = .1

- $50!/((5!)^{10}) * .1^{50} = 0.0000005$


### B

$.0338 = p(y=0) + p(y = 1)$


## 11

### A

- $p(y) = p*q^{y-1}$

### B

- $1/{.4} = 2.5 = 1/p$

### C

- $p(y) = .4/.6^{0} = 0.4$

### D

- $p(y=2)$


## 12

### A

- ${nr}/N = 80/209 = .3828$

### B

- ${\binom{8}{4}*\binom{201}{6} }/ \binom{209}{10}$ = 0.00017


## 13

### A

- $sigma^{2} = .03$

### B

- The events need to occur in a specific unit of time,
- The units are all indepdent of each other. 

### C

$y = {.03^{0} * e^{-.03}}/{0!} = .9704$

## 14

### A
$2c -yc$ 
$\int_0^1$ 
$f(y)dy=1$
$ c = 2/3$

### B

The CDF is .1 which is the result of the integral below. 
$F(y) = \int_ {-\infty}^yf(x)dx = \int_0^yf(x)dx$

### C

$2/3 * (2*(.4)) - .4^{2}/{2}$ = .48

### D

$2/3 * (2(.6) - .6^{2}/2) - 2/3 (2(.1) - .1^2/2)  = 0.55$


## 15 

### A

$f(y) = \frac{3}{20} -\frac{3y^2}{500}$

mean: $\mu = E(Y) = \int_{-5}^{5}y(\frac{3}{20} -\frac{3y^2}{500})dy=\int_{-5}^{5}(\frac{3y}{20} -\frac{3y^3}{500})dy = \frac{3}{20}\int_{-5}^{5}ydy - \frac{3}{500}\int_{-5}^5y^3dy = 0$

variance: $E(Y^2) -\mu^2$, need to find $E(Y^2) = \int_{-5}^{5}y^2(\frac{3}{20} -\frac{3y^2}{500})dy = 5$

$E(Y^2) -\mu^2 = 5 - 0 = 5$

Thus, $\mu = 0,\sigma^2 = 5$

### B

- Redo the steps from part A, except dividing by 60 minutes to convert the time into hours. 

mean: $E(\frac{1}{60}Y) = \frac{1}{60}E(Y) = 0$ so $\mu = 0$

Variance: $E(\frac{1}{60^2}Y^2) = \frac{1}{60^2}E(Y^2) = \frac{5}{60^2}= .0014$

### C

- C is the exact same as B except multipling by 60 instead of dividing by 60. 

mean: $\mu = E(60Y) = 60E(Y) = 60\times0 = 0$

variance: $E(60Y^2) = 60^2E(Y^2) = 60^2\times5 = 18000$

## 16

### A

```{r}
1-pnorm(-1.5625,0,1)
```

### B

```{r}
pnorm(1.5625,0,1)
```

### C

```{r}
pnorm((2)/3.2,mean=0,sd=1) - pnorm(1/3.2,0,1)
```


## 17

### A

```{r}
pnorm(700,605,185)-pnorm(500,605,185)
```

### B

```{r}
pnorm(500,605,185)-pnorm(400,605,185)
```

### C

```{r}
pnorm(850,605,185)
```


### D

```{r}
1-pnorm(1000,605,185)
```

### E

```{r}
185*(605 + qnorm(.9,0,1))
```
